Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Data

### 2019-01-30 article.Rnw
Add acknowledments and update submitted version
Typo

Furthermore, results in \autoref{tab:coef-cotton} also show the
advantage of the COM-Poisson$_\mu$ model, since the regression parameter
estimates are quite similar to those obtained for the Poisson model,
whereas estimates from the original COM-Poisson model are on a different
and not easily interpreted scale.  The ratios between estimates and
their respective standard errors for the two COM-Poisson models are very
close to ratios from the y quasi-Poisson model. However, it is important
to note that COM-Poisson model is a full parametric approach, i.e. there
is a probability distribution associated to the counts, while the
quasi-Poisson model is based only on second-moment assumptions.

@@

>>>>

Furthermore, results in \autoref{tab:coef-cotton} also show the
advantage of the COM-Poisson$_\mu$ model, since the regression parameter
estimates are quite similar to those obtained for the Poisson model,
whereas estimates from the original COM-Poisson model are on a different
and not easily interpreted scale.  The ratios between estimates and
their respective standard errors for the two COM-Poisson models are very
close to ratios from the quasi-Poisson model. However, it is important
to note that COM-Poisson model is a full parametric approach, i.e. there
is a probability distribution associated to the counts, while the
quasi-Poisson model is based only on second-moment assumptions.

@@

\section*{Acknowledgments}

The authors wish to thank the anonymous referees for many comments from
which this paper has benefited. This work was partially supported by
CNPq, a Brazilian science funding agency.
